The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-31 ms.Rmd
Small plotting change.
Match capitilisation in workflow names.

```{r fengworkCaptions, eval = TRUE, echo = FALSE}
fengworkcap <- '
  Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence).
  White areas are masked due to being marine or due the MESS mask [@Elith2010]
'

@@

```{r fengChangeWorkflow, eval = TRUE, fig.show = 'hide'}
Feng_Papes_interactive <- 
  ChangeWorkflow(workflow = Feng_Papes,
                   output = Chain(PerformanceMeasures, 
                                  PrintMap, 
                                  InteractiveMap, 
                                  ResponseCurve))
```

@@

All of these have now been uploaded to the ZOON modules repository (under the names `CarolinaWrenPO`, `CarolinaWrenPA`, and `MaxLike`), though we diusplay the code required for the module `CarolinaWrenPO` here as an illustration of the minimal overhead required in writing `zoon` software modules:

@@

```{r merowworkflow, eval = FALSE}
merow_and_silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = ...,
    process = ...,
    model = list(MaxEnt, MaxLike),
    output = ...)
```

@@

```{r mewoChangeWorkflow, eval = FALSE}
merow_and_silander_spatial <- ChangeWorkflow(
    merow_and_silander,
    process = Chain(..., PartitionDisc))
```

>>>>

```{r fengworkCaptions, eval = TRUE, echo = FALSE}
fengworkcap <- '
  Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence).
  White areas are masked due to being marine in the marine environment or due to the MESS mask [@Elith2010]
'

@@

```{r fengChangeWorkflow, eval = TRUE, fig.show = 'hide'}
Feng_Papes_Interactive <- 
  ChangeWorkflow(workflow = Feng_Papes,
                   output = Chain(PerformanceMeasures, 
                                  PrintMap, 
                                  InteractiveMap, 
                                  ResponseCurve))
```

@@

All of these have now been uploaded to the ZOON modules repository (under the names `CarolinaWrenPO`, `CarolinaWrenPA`, and `MaxLike`), though we display the code required for the module `CarolinaWrenPO` here as an illustration of the minimal overhead required in writing `zoon` software modules:

@@

```{r merowworkflow, eval = FALSE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = ...,
    process = ...,
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = ...)
```

@@

```{r mewoChangeWorkflow, eval = FALSE}
Merow_Silander_Spatial <- ChangeWorkflow(
    merow_and_silander,
    process = Chain(..., PartitionDisc))
```
